---
title: "Lists - In Class Exercises"
author: "Adam Gullion"
date: "DATA 2401"
output: html_document
---

# Exercises:

Make a list that contains the information on a single playing card. Suit, face, and value.

```{r}
clubs_of_7 <- list(
  Suit = ("club"),
  face = (7),
  value = (7)
)
clubs_of_7
str(clubs_of_7)


```

Make a second list where each element contains all the options for suit, face, and value, respectively.

```{r}
card_possibilities<- list(
  suit = c("heart","club","spade","diamond"),
  face = c(1:10,"Jack","Queen","King"),
  value =c(1:10,10,10,10)
)
card_possibilities
str(card_possibilities)

mean(card_possibilities[["value"]])
(card_possibilities$face)
mean(card_possibilities$value)
```

If `Newlist <- list(a=1:10, b="Good morning", c="Hi")`, write an R statement that will add 1 to each element of the first vector in Newlist.

```{r}
Newlist <- list(a=1:10, b="Good morning", c="Hi")
Newlist [[1]]<- Newlist[[1]]+1
Newlist[[1]]
mean(Newlist[[1]])

```

If `b <- list(a=1:10, c="Hello", d="AA")`, write an R expression that will get all elements of the first vector of b, except the second, and write another that returns only elements of `a` that are greater than 7.

```{r}
b <- list(a=1:10, c="Hello", d="AA")
b [[1]] !=2

b$a[-2]
b$a[b$a>7]
```

Let `x <- list(a=5:10, c="Hello", d="AA")`, write an R statement to add a new item z = "NewItem" to the list x.

```{r}
x <- list(a=5:10, c="Hello", d="AA")
x$z<-"new item"

lapply(x$a,round)

print(x)

```


